---
title: "Lab 9"
author: Jacky Wu
format: 
  html:
    self-contained: true
execute: 
  echo: true
  message: false
  warning: false
---

# Setup

```{r}
#| message: false
library(tidyverse)
state_a <- read_csv(here::here("supporting_artifacts" , "Datasets" , "StateNames_A.csv")) %>% 
  rename(Sex = Gender)
```

# Summarizing & Visualizing the Number of Allisons

## 1.

```{r}
state_allison <- state_a %>% 
  filter(Name == 'Allison') %>% 
  pivot_wider(names_from = Sex, 
              values_from = Count) %>% 
  mutate(M = replace_na(
    M, 0)
  ) %>% 
  group_by(State) %>% 
  summarize(across(
    'F':'M', .fns = sum)
  )
state_allison
```

## 2.

```{r}
state_female <- state_a %>% 
  filter(Sex == 'F')
```

## 3.

```{r}
allison_year <- state_female %>% 
  filter(Name == 'Allison') %>% 
  group_by(Year) %>% 
  summarize(across(
    'Count', .fns = sum)
  )
allison_year
```

```{r}
ggplot(data = allison_year, 
       mapping = aes(
         x = Year, y = Count)
       ) +
  geom_line() +
  labs(x = 'Year', y = '', 
  title = 'Number of Babies Named Allison per Year')
```

# Modeling the Number of Allisons

## 4.

```{r}
allison_mod <- allison_year %>% 
  lm(Count ~ Year, data = .)
```

## 5.

```{r}
#| message: false
ggplot(data = allison_year, 
       mapping = aes(
         x = Year, y = Count)
       ) +
  geom_point() +
  stat_smooth(method = "lm") +
  labs(x = 'Year', y = '', 
  title = 'Regression Model Predicting Number of Babies Named Allison Using Year')
```

## 6.

```{r}
summary(allison_mod)
```

The estimate regression equation is:

Count = 209689.76 - 101.52(Year)

## 7.

```{r}
allison_df <- broom::augment(allison_mod)
```

```{r}
ggplot(data = allison_df, 
       mapping = aes(x = .fitted, y = .resid)
       ) +
  geom_point() +
  labs(x = 'Fitted', y = '', 
  title = 'Residual Vs. Fitted Model')
```

Looking at the residual plot, there seems to be a curvature pattern which means that a linear model might not be the best fit for our model.

## 8.

It does seem like the name Allison isn't as cool as it used to be. Our regression model shows that the predicted number of babies named Allison decreases by 101.52 as year increases by one. However, we need to be cautious with this conclusion since our residual plot shows a curvature pattern, which means that a linear model is not the best fit for our model.

# Spelling By State

## 9.

```{r}
state_allan <- state_a %>% 
  filter(Sex == 'M',
         Name %in% c(
           'Allan', 'Alan', 'Allen')
         )
```

```{r}
#| message: false
allan_year <- state_allan %>% 
  group_by(Name, Year) %>% 
  summarize(across(
    'Count', .fns = sum)
  )
```

```{r}
ggplot(data = allan_year, 
       mapping = aes(
         x = Year, y = Count, color = Name)
       ) +
  geom_line() +
  labs(x = 'Year', y = '', 
  title = 'Number of Babies Named Alan, Allen, and Allan per Year')
```

## 10.

```{r}
allan_PA_CA <- state_allan %>% 
  filter(Year == 2000,
         State %in% c(
           'PA','CA')
         ) %>% 
  mutate(Count = replace_na(
    Count, 0)
    ) %>% 
  pivot_wider(names_from = Name, 
              values_from = Count)
allan_PA_CA
```

## 11.

```{r}
allan_percent <- allan_PA_CA %>%
  mutate(Total = rowSums(across(
    'Alan':'Allan')
    ),
    Alan = Alan/Total*100,
    Allen = Allen/Total*100,
    Allan = Allan/Total*100,
  ) %>% 
  select(-Total)
allan_percent
```

I wanted to create a total column by adding the rows and this source helped me with this:

https://stackoverflow.com/questions/3991905/sum-rows-in-data-frame-or-matrix

For CA, the percent breakdowns for the three names are 65.35% for Alan, 19.85% for Allen, and 14.79% for Allan.

For PA, the percent breakdowns for the three names are 42.86% for Alan, 47.05% for Allen, and 10.08% for Allan.

This shows that Allan's spelling of his name is unusual even in his home state of PA, having only 10% of people with this spelling out of the three names.
